Resilience and Home-Space for WSTS

### 2024-01-05 diapo/presentation.tex
up

>>>>

   \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Ingredient 2: link with coverability}

  \begin{block}{ }
   $s_j$ is coverable from $x$ in $\mathscr{S}$ if and only if $\mathop{\downarrow} s_j$ is coverable (for inclusion) from $\mathop{\downarrow} x$ in $\hat{\mathscr{S}} $ 
 \end{block}

  \begin{block}{ }
The resilience problem can be reduced to the following infinite number of instances of the coverability problem in $\mathscr{S}$: for all $x \in \Bad$ does there exist an $j$ such that $s_j$ is coverable from $x$. Let us show how this infinite set of coverability questions can be reduced to a \emph{finite} set of coverability questions in the completion $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ of $\mathscr{S}=(S,\rightarrow, \leq)$. 
 \end{block}

    \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Ingredient 3 (only for $k$-resilience)}

     \todo[inline,color=blue!20]{ 
  ... actually it is generally over now maybe we don't have to go into all the details here
}
